Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-02-09 paper/main.tex
SI: ode vs binomial

Results are shown in Table~\ref{tab:pcn-robustness}. The $I_\varepsilon$ indicators shows that, regardless of the budget, the decision maker will lose at worst a $0.050$ normalized return in any of the objectives. On average, it will lose $0.010$ returns. Moreover, we emphasize that the learned coverage set contains the non-dominated returns across the whole training procedure. Since the Binomial model is stochasticity, for multiple executions of the same policy, the executions that remains in the coverage set is the one with advantageous transitions due to this stochasticity. Thus, we expect our policy-executions to obtain slightly worse results than the target-solution selected from the coverage set. In light of this, we conclude that the policies trained by PCN are reliable and produce returns as close as possible from their chosen target.

@@

\section{Additional results}
\subsection{Learned coverage sets}

>>>>

Results are shown in Table~\ref{tab:pcn-robustness}. The $I_\varepsilon$ indicators shows that, regardless of the budget, the decision maker will lose at worst a $0.050$ normalized return in any of the objectives. On average, it will lose $0.010$ normalized returns. Moreover, we emphasize that the learned coverage set contains the non-dominated returns across the whole training procedure. Since the Binomial model is stochasticity, for multiple executions of the same policy, the executions that remains in the coverage set is the one with advantageous transitions due to this stochasticity. Thus, we expect our policy-executions to obtain slightly worse results than the target-solution selected from the coverage set. In light of this, we conclude that the policies trained by PCN are reliable and produce returns as close as possible from their chosen target.

@@

\section{Additional results}

\subsection{Comparison of coverage sets learned on ODE and Binomial models}
\subsection{sec:cs-ode-vs-binomial}

\begin{figure}
    \centering
    \input{fig/arh_binomial_ode}
    \caption{ODE vs Binomial}
    \label{fig:pf-binomial-ode}
\end{figure}

The coverage sets displayed in Figure~\ref{fig:pf-binomal-arh-budgets} correspond to PCN trained on the Binomial model. To show that PCN copes with the stochasticity of this model, we compare these coverage sets with the ones learned on the ODE model.

Results are shown in Figure~\ref{fig:pf-binomial-ode}. First, in a similar fashion as Figure~\ref{fig:pf-binomal-arh-budgets}, we show the interpolated average coverage set for different budget setting, with PCN trained on the ODE model. We observe similar trends as for the Binomial model. Next, for each budget setting, we compare the interpolated average coverage set of the Binomial setting with the ODE setting. We observe similar coverage set, regardless of the budget setting, indicating that PCN is able to cope with stochastic transitions.

\subsection{Learned coverage sets}
